\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models

### 2023-01-10 paper/fse23/intro.tex
rewrite intro

To address this limitation, methodologies to assess an NLP model on a set of
  linguistic capabilities have been introduced~\cite{marcoACL2020checklist,rottger2020hatecheck}. 
A \lc
explains a functionality of the input and output behavior for the
NLP model under test. Typically, it describes certain type of inputs
and outputs observed in real world for the target NLP task.
% , ranging
% from simple to complicated behaviors.
Testing the linguistic capabilities allows the model developers to better understand the capabilities and potential issues of the NLP
models. 
For example,  \Cklst~\cite{marcoACL2020checklist}, a behavioral testing framework for evaluating NLP models, defines a linguistic capability called ``Negated neutral should still be neutral'' to measure how accurately a \sa model understands that the negated neutral input has neutral sentiment
\cite{marcoACL2020checklist}. 
It requires the \sa model to
output neutral sentiment on the negated neutral inputs. 
Such evaluation methodology avoids the overestimation of the model performance as it measures the model performance on each functionality.
% ,and the separate model performance
% explain distribution of the performance over the linguistic capabilities
In the end, testing through linguistic capabilities provides not only the overall model performance, but also the malfunction facets of the model.

>>>>

\jl{To address this limitation, increasing number of evaluation
  methodologies has been conducted to measure and obtain the
  trustworthiness of a NLP model. First, as the NLP model is still
  fragile to adversarial attacks and decreases trustworthness of the
  NLP model, adversarial examples of the model generated by
  perturbations to the input are used to measure the robustness of the
  model.~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack,udeshi2019ogma}. Also,
  fairness, specific bias in the NLP model such as gender and races,
  has been
  evaluated~\cite{soremekun2020astraea,udeshi2018fairnesstest}. Additionally,
  methodologies to assess an NLP model on a set of \lcs have been
  introduced~\cite{marcoACL2020checklist,rottger2020hatecheck}. Compared
  with the aforementioned testing aspects, a \lc explains a more
  comprehensive functionalities of the input and output behavior for
  the NLP model under test. Typically, it describes certain type of
  inputs and outputs observed in real world for the target NLP task.
}
% , ranging
% from simple to complicated behaviors.
Testing the linguistic capabilities allows the model developers to
better understand the capabilities and potential issues of the NLP
models.  For example, \Cklst~\cite{marcoACL2020checklist}, a
behavioral testing framework for evaluating NLP models, defines a
linguistic capability called ``Negated neutral should still be
neutral'' to measure how accurately a \sa model understands that the
negated neutral input has neutral sentiment
\cite{marcoACL2020checklist}.  It requires the \sa model to output
neutral sentiment on the negated neutral inputs.  Such evaluation
methodology avoids the overestimation of the model performance as it
measures the model performance on each functionality.
% ,and the separate model performance
% explain distribution of the performance over the linguistic capabilities
In the end, testing through linguistic capabilities provides not only
the overall model performance, but also the malfunction facets of the
model.
